Dominance Regions for Rank Two Cluster Algebras

### 2022-08-04 Annals of Combinatorics/submission.tex
Authors and abstract

\author[1]{\fnm{Dylan} \sur{Rupel}}\email{rupel.dylan@pusd.us}

\author[2]{\fnm{Salvatore} \sur{Stella}}\email{salvatore.stella@univaq.it}

@@

\abstract{We study the polygons defining the dominance order on $\bfg$-vectors in cluster algebras of rank 2.}

>>>>

\author*[1]{\fnm{Dylan} \sur{Rupel}}\email{rupel.dylan@pusd.us}

\author*[2]{\fnm{Salvatore} \sur{Stella}}\email{salvatore.stella@univaq.it}

@@

\abstract{We study the polygons defining the dominance order on $\bfg$-vectors in cluster algebras of rank 2.\hfill~}
